---
title: "Data 605 Homework 3"
author: "Jenny"
date: "February 17, 2018"
output: html_document
---

install.packages("pracma")

####Problem Set 1

##### (1) What is the rank of the matrix A?

$$\mathbf{A} = \left[\begin{array}
{}
1 & 2 & 3 & 4\\
-1 & 0 & 1 & 3\\
0 & 1 & -2 & 1\\
5 & 4 & -2 & -3\\
\end{array}\right]
$$


```{r}
A <- matrix(c(1, 2, 3, 4, -1, 0, 1, 3, 0, 1, -2, 1, 5, 4, -2, -3), nrow = 4, ncol = 4, byrow = TRUE)
A
y <- qr(A)

rank <- y$rank

rank

```
##### The rank of A is 4.

##### (2) Given an mxn matrix where m > n, what can be the maximum rank? The minimum rank, assuming that the matrix is non-zero?

##### If A is m x n, it follows the inequalities that 
$$\\rank(A_{max})\leq min(m , n)
$$

#####Therefore, the maximum rank is n, and the minimum rank is 1.

##### (1) What is the rank of the matrix B?
$$\mathbf{B} = \left[\begin{array}
{}
1 & 2 & 1\\
3 & 6 & 3\\
2 & 4 & 2\\
\end{array}\right]
$$

```{r}
B <- matrix(c(1, 2, 1, 3, 6, 3, 2, 4, 2), nrow = 3, ncol = 3, byrow = TRUE)
B
z <- qr(B)

rank <- z$rank

rank

```

##### The rank of B is 1.

####Problem Set 2

$$\mathbf{A} = \left[\begin{array}
{}
1 & 2 & 3\\
0 & 4 & 5\\
0 & 0 & 6\\
\end{array}\right]
$$

```{r}

library(pracma)
A <- matrix(c( 1, 2, 3, 0, 4, 5, 0, 0, 6), nrow = 3, ncol = 3, byrow = TRUE)
A

p <- charpoly(A, info = TRUE)
p$cp
```
#####Therefore, the characteristic polynomial is 
$$\lambda^3\ - 11\lambda^2\ + 34\lambda\ - 24 = 0$$

```{r}
ev <- eigen(A)
values <- ev$values
values
```
$$\lambda = 6, 4,1
$$
```{r}
vec <- ev$vectors
vec
```
$$when\quad \lambda = 6,
$$

$$\mathbf span ({E_{\lambda = 6}} = \left[\begin{array}
{}
0.5108407 \\
0.7981886 \\
0.3192754 
\end{array}\right])
$$

$$when\quad \lambda = 4,
$$

$$\mathbf span ({E_{\lambda = 4}} = \left[\begin{array}
{}
0.5547002 \\
0.8320503 \\
0 
\end{array}\right])
$$

$$when\quad \lambda = 1,
$$

$$\mathbf span ({E_{\lambda = 1}} = \left[\begin{array}
{}
1 \\
0 \\
0 
\end{array}\right])
$$
