---
title: "Data605_HW6"
author: "Jenny"
date: "March 18, 2018"
output: html_document
---

##### 1. Let X1, X2, . . . , Xn be n mutually independent random variables, each of which is uniformly distributed on the integers from 1 to k. Let Y denote the minimum of the Xi's. Find the distribution of Y .

```{r setup, include=TRUE}
k <- 30
Y <- list()
i <- 1

for(i in 1:100) {
  x <- sample(k, 1, replace = TRUE)
  Y[length(Y) + 1] <- list(min(x))
  i <- i + 1
}

hist(as.numeric(Y))
```
##### When the sample size is 100, the distribution of Y is showing in the graph, which does not show much pattern of any distribution. However, when the size of number is increased from 100 to 10000. Let's see.
```{r }
k <- 30
Y <- list()
i <- 1

for(i in 1:100000) {
  x <- sample(k, 1, replace = TRUE)
  Y[length(Y) + 1] <- list(min(x))
  i <- i + 1
}

hist(as.numeric(Y))
```
##### The distribution is discrete uniform distribution too.

##### Your organization owns a copier (future lawyers, etc.) or MRI (future doctors). This machine has a manufacturer's expected lifetime of 10 years. This means that we expect one failure every ten years. (Include the probability statements and R Code for each part.).
##### a. Geometric Distribution

$$\ Expected = 10$$

$$\ Prob = \frac{1}{Expected} = 0.1$$
$$\ Probability  = (1-Prob)^{n-1} Prob$$

```{r }
E <- 10
Prob <- 1/E
Prob_fail_8 <- (1- Prob)^(8) * Prob
Prob_fail_8
#The probability that the machine will fail after 8 years is 0.04304672.

# Expected values is 10 and standard deviation is 90.
sd <- (1-Prob)/(Prob^2)
sd
```

##### b. Exponential Distribution

$$\ P(X > 8) = e^{-8/10} $$
```{r }

Prob <- exp(-8/10)
Prob
#The probability that the machine will fail after 8 years is 0.449329. The standard deviation is equal to mean, which is 10.
```

##### c. binomial distribution

```{r}

Prob <- choose(9, 8) * 0.5^8 * (1 - 0.5)^1
Expected <- 9*0.5
sd <- sqrt(9 * 0.5 * (1-0.5))
sd
#The probability that the machine will fail after 8 years is 0.0175. The expected value is 4.5, and the standard deviation is 1.5
```


##### d. Poisson Distribution
```{r}
ppois(8, lambda = 10, lower.tail = FALSE)
Expected <- 10
sd <- sqrt(10)
sd
#The probability that the machine will fail after 8 years is 0.6672. The expected value is 10, and the standard deviation is 3.16.
```
$$\ \lambda= 10$$

